The Name of the Title is Hope

### 2023-07-26 input/2_introduction.tex

Having a sense of agency means experiencing being in control of our own voluntary actions, instead of them feeling as though they randomly happen to us. It has frequently been shown that if users have a strong sense of agency, they are more likely to feel engaged and satisfied with an interaction, and are more likely to trust a system~\citep{Berberian2012-do, Miller2007-rb}. The key challenge to drive adoption of human \textit{action augmentation} then is to design for agency experience, so users feel as though they are in the ``driver's seat'' once again.
% if something happens for you in an interaction there is a cost to that:
% - impacts sense of agency which in turn may makes user's engage less -> citation?
% - may impact precision and accuracy, which can be very critical in high stakes scenarios, e.g. air traffic control -> citation?

% 3. Question
% Asks the question how the hurdles of the Complication can be overcome. How can we prevent the threat or seize the opportunity? Also, what would be the benefits if the complication would be overcome?
% What have others done to address this and what do we propose "instead"
Previously, ~\citet{Kasahara2019-sk} have shown that reaction times when tapping a stimuli on a touchscreen can be reduced by augmenting the user with EMS while maintaining their sense of agency. The authors found a relation between the experience of agency and the \textit{pre-emptive} gain, i.e., how much earlier the action of the user could be elicited. However, setting this gain factor only works in stimulus-response scenarios where the user behavior can be predicted with high accuracy. A key question then remains: How can we maintain agency during physical action augmentation without controlling the environment? In other words, how can we design a closed-loop system to deliver an integrated, \textit{natural}, experience for users' augmented actions?
% At around 80 ms preceding the naturally occurring action, user's integrate the augmentation and maintain an experience of agency.

@@

% 4. (short) Answer Teaser
% Provides the answer on how to overcome the hurdles. Explains how this will help deflect the threats or seize the opportunities.
% keep this short
In this paper, we present a fast communication channel between a user's brain signals and a physical end effector, here EMS. Crucially, our brain-computer interface controls the user's muscles through EMS at the time of their \textit{intent to act}, as measured through readiness potentials (RP) present in the user's electroencephalogram (EEG). In our user study we applied a mixed-methods research approach to investigate whether keeping the physical impact on the user's body in line with their intention to move preserves their sense of agency.
% We found ... rendering the augmentation a \textit{natural}, integrated expansion of the user's body.

>>>>

Having a sense of agency means experiencing being in control of our own voluntary actions, instead of them feeling as if they randomly happen to us. It has frequently been shown that if users have a strong sense of agency, they are more likely to feel engaged and satisfied with an interaction, and are more likely to trust a system~\citep{Berberian2012-do, Miller2007-rb}. The key challenge to drive adoption of human \textit{action augmentation} then is to design for agency experience, so users feel as though they are in the ``driver's seat'' when using such an augemntation system.
% if something happens for you in an interaction there is a cost to that:
% - impacts sense of agency which in turn may makes user's engage less -> citation?
% - may impact precision and accuracy, which can be very critical in high stakes scenarios, e.g. air traffic control -> citation?

% 3. Question
% Asks the question how the hurdles of the Complication can be overcome. How can we prevent the threat or seize the opportunity? Also, what would be the benefits if the complication would be overcome?
% What have others done to address this and what do we propose "instead"
Previously, ~\citet{Kasahara2019-sk} have shown that reaction times when tapping a stimulus on a touchscreen can be reduced by augmenting the user with EMS while maintaining their sense of agency. The authors found a relation between the experience of agency and the \textit{pre-emptive} gain, i.e., how much earlier the action of the user could be elicited. However, setting this gain factor only works in stimulus-response scenarios where the user behavior can be predicted with high accuracy. A key question then remains: How can we maintain agency during physical action augmentation without controlling the environment? In other words, how can we design a closed-loop system to deliver an integrated, \textit{natural}, experience for users' augmented actions?
% At around 80 ms preceding the naturally occurring action, user's integrate the augmentation and maintain an experience of agency.

@@

% 4. (short) Answer Teaser
% Provides the answer on how to overcome the hurdles. Explains how this will help deflect the threats or seize the opportunities.
% keep this short
In this paper, we present a fast communication channel between a user's brain signals and a physical end effector, here EMS. Crucially, our brain-computer interface controls the user's muscles through EMS at the time of their \textit{intent to act}, as measured through readiness potentials (RP) present in the user's electroencephalogram (EEG). In our user study, we applied a mixed-methods research approach to investigate whether keeping the physical impact on the user's body in line with their intention to move preserves their sense of agency.
% We found ... rendering the augmentation a \textit{natural}, integrated expansion of the user's body.

### 2023-07-26 input/6_results.tex

\subsection{Agency}
\missingfigure{A: Boxplot of questionnaire scores, are they significantly better than 0? Are they significantly better then after the training? -> frame the training the same as the experiment, B: Sentiment Word Clouds}

>>>>

\subsection{Agency}
\missingfigure{A: Boxplot of questionnaire scores of three Blocks (block 2 grey, because not intention given) - play around with visualization of words that were used to explain control rating. B. Boxplots intentional binding (maybe integrate A and B) C. more subjective evaluation of interview / maybe world cloud / maybe sentiment analysis) }
